A survey of HTTP caching options on the open Web

### 2015-01-05 sanity/paper1.tex
distribution of freshness time
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@940 43ef1190-90fd-4dd7-a769-d0121f02b80e

@@

>>>>

A\todo{Do I need details on how to compute the freshness lifetime?}

@@

\subsection{Distribution of freshness time}

We next examine the freshness lifetime of the 2965 information
resources that returned a successful response, either with SPARQL
results or RDF data. 405 returned valid headers, but 114 did so to
\emph{prohibit} caching of the response, and 3 contained conflicting
headers, i.e. set an freshness lifetime, but also prohibited
caching. Additionally, 269 resources had a \httph{Cache-Control}
header to control other aspects of caching than lifetime, i.e. to say
that only private caches may use the response, that the cache must be
revalidated, or to prohibit caching.

Caching may prohibited by setting a non-positive freshness
lifetime. Common practice is to set the \httph{Expires} header to a
date far back in time, which has also been done in large parts of the
present dataset. For the following, we have set any non-positive
lifetime to 0, as that is semantically equivalent. With that, we
obtain the summary statistics in Table~\ref{tab:summaryhard}. In
figure\todo{add figure}, we have included a histogram with the counts
of the resources that had 0 lifetime, and then boxes of varying length.

\begin{table}[ht]
\begin{center}
\caption{Summary statistics for standards-compliant freshness lifetime}\label{tab:summaryhard}
\begin{tabular}{lr}
Min.   &       0   \\ 
1st Qu.&       0   \\ 
Median &     600   \\ 
Mean   &  583003   \\ 
3rd Qu.&  172800   \\ 
Max.   & 52702521   \\ 
   \hline
\end{tabular}
\end{center}
\end{table}
